Live Functional Programming with Typed Holes

### 2018-10-31 calculus.tex
typos

The supplemental material includes our Agda
mechanization  \cite{norell2009dependently,norell:thesis,Aydemir:2005fk}
of the semantics and metatheory of \HazelnutLive,
%including proofs of all of the
including all of the theorems stated above and necessary lemmas.
%
%We choose the
%(as did the mechanization of \Hazelnut by \citet{popl-paper}, though only a few definitions are common).
%
%Agda is a good choice because it is designed to explicitly communicate a proof's structure, as is our goal, rather than relying on proof automation.
%
%Agda itself was also an inspiration for this work because it supports holes, albeit in a more limited form than described here (cf. Sec.~\ref{sec:intro}).
%
%
Our approach is standard: we model judgements as
inductive datatypes, and rules as dependently typed constructors of these judgements.
%
We adopt Barendregt's convention for bound variables \cite{urban,barendregt84:_lambda_calculus} and hole names, and avoid certain other complications relted to substitution by enforcing the requirement that all bound variables in a term are unique when convenient (this requirement can always be discharged by alpha-variation). We encode typing
contexts and hole contexts using metafunctions.
To support this encoding choice, we postulate function extensionality (which is independent of Agda's axioms) \cite{awodey2012inductive}. We encode finite substitutions as an inductive datatype with a base case representing the identity substitution and an inductive case that records a single substitution. Every finite substitution can be represented in this scheme. This makes it easier for Agda to see why certain inductions that we perform are well-founded.  
The documentation provided with the mechanization has more details.

@@

The \Hazel implementation described in Sec.~\ref{sec:examples}
includes an unoptimized interpreter, written in OCaml, that implements the semantics as described
in this section, with some simple extensions. As with many full-scale systems, there is not currently a formal
specification for the full \Hazel language, but the \appendixName
discusses how the standard approach for deriving a ``gradualized'' version of a
language construct provides most of the necessary scaffolding \cite{DBLP:conf/popl/CiminiS16}, and provides some examples (sum types and numbers).

>>>>

The supplemental material includes our Agda
mechanization  \cite{norell2009dependently,norell:thesis,Aydemir:2005fk}
of the semantics and metatheory of \HazelnutLive,
%including proofs of all of the
including all of the theorems stated above and necessary lemmas.
%
%We choose the
%(as did the mechanization of \Hazelnut by \citet{popl-paper}, though only a few definitions are common).
%
%Agda is a good choice because it is designed to explicitly communicate a proof's structure, as is our goal, rather than relying on proof automation.
%
%Agda itself was also an inspiration for this work because it supports holes, albeit in a more limited form than described here (cf. Sec.~\ref{sec:intro}).
%
%
Our approach is standard: we model judgements as
inductive datatypes, and rules as dependently typed constructors of these judgements.
%
We adopt Barendregt's convention for bound variables \cite{urban,barendregt84:_lambda_calculus} and hole names, and avoid certain other complications related to substitution by enforcing the requirement that all bound variables in a term are unique when convenient (this requirement can always be discharged by alpha-variation). We encode typing
contexts and hole contexts using metafunctions.
To support this encoding choice, we postulate function extensionality (which is independent of Agda's axioms) \cite{awodey2012inductive}. We encode finite substitutions as an inductive datatype with a base case representing the identity substitution and an inductive case that records a single substitution. Every finite substitution can be represented this way. This makes it easier for Agda to see why certain inductions that we perform are well-founded.  
The documentation provided with the mechanization has more details.

@@

The \Hazel implementation described in Sec.~\ref{sec:examples}
includes an unoptimized interpreter, written in OCaml, that implements the semantics as described
in this section, with some simple extensions. As with many full-scale systems, there is not currently a formal
specification for the full \Hazel language, but the \appendixName~
discusses how the standard approach for deriving a ``gradualized'' version of a
language construct provides most of the necessary scaffolding \cite{DBLP:conf/popl/CiminiS16}, and provides some examples (sum types and numbers).
